Towards human SuperEEG

### 2018-10-10 paper/main.tex
updated stats for results

Although both datasets we examined provide good full-brain coverage
(when considering data from every patient; e.g.\
Fig.~\ref{fig:corrmap}C, D), electrodes are not placed uniformly
throughout the brain.  For example, electrodes are more likely to be
implanted in regions like the medial temporal lobe (MTL), and are
rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
MNI152 brain, we computed the proportion of electrodes in the dataset
that were contained within a 20 MNI unit radius sphere centered on
that voxel.  We defined the \textit{density} at that location as this
proportion.  Across Datasets 1 and 2, the electrode placement
densities were similar (correlation by voxel:
$r = XXX, p = XXX$).  We wondered whether regions with good
covererage might be associated with better reconstruction accuracy
(e.g. Fig.~\ref{fig:corrmap}C, D indicate that many electrodes in the
MTL have relatively high reconstruction accuracy, and occipital
electrodes tend to have relatively low reconstruction accuracy).  To
test whether this held more generally across the entire brain, for
each dataset we computed the electrode placement density for each
electrode from each patient (using the proportion of \textit{other}
patients' electrodes within 20 MNI units of the given electrode).  We
then correlated these density values with the across-patient
reconstruction accuracies for each electrode.  Contrary to our
expectation, rather than positive correlations, we found weak (but
reliable) negative correlations between reconstruction accuracy and
density for both datasets (Dataset 1: $r = XXX, p = XXX$; Dataset 2:
$r = -0.16, p < 10^{-10}$).  This indicates that the reconstruction
accuracies we observed are not driven solely by sampling density, but
rather may also reflect higher order properties of neural dynamics
such as functional correlations between distant
voxels~\citep{BetzEtal17b}.

@@

To gain insights into whether particular electrode locations might be
especially informative, we first computed the average reconstruction
accuracy across all of each patient's electrodes (using the
across-patients cross validation test; black histograms in
Fig.~\ref{fig:corrmap}A and B).  We labeled each patient's electrodes
in each dataset with the average reconstruction accuracy for that
patient.  In other words, we assigned every electrode from each given
patient the same value, reflecting how well the activity patterns at
those electrodes were reconstructed on average.  Next, for each voxel
in the 4~mm$^3$ MNI brain, we computed the average value across any
electrode (from any patient) that came within 20 MNI units of that
voxel's center.  Effectively, we computed an \textit{information
  score} for each voxel, reflecting the average reconstruction
accuracy across any patients with electrodes near each voxel-- where
the averages were weighted to reflect patients who had more electrodes
implanted near that location. This yielded a single map for each
dataset, highlighting regions that are potentially promising
implantation targets in terms of providing full-brain activity
information via SuperEEG (Fig.~\ref{fig:informap}A, B).  Despite task
and patient differences across the two datasets, we nonetheless found
that the maps of the most promising implantation targets derived from
both datasets were similar (voxelwise correlation between information
scores across the two datasets: $r = XXX, p = XXX$).  While the
correspondence between the two maps was not perfect, our finding that
there were some commonalities between the two maps lends support to
the notion that different brain areas are differently informative
about full-brain activity patterns.  Further, regions like XXX, XXX,
and XXX that exhibited strong information scores in both datasets may
be especially promising implantation targets.

>>>>

Although both datasets we examined provide good full-brain coverage
(when considering data from every patient; e.g.\
Fig.~\ref{fig:corrmap}C, D), electrodes are not placed uniformly
throughout the brain.  For example, electrodes are more likely to be
implanted in regions like the medial temporal lobe (MTL), and are
rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
MNI152 brain, we computed the proportion of electrodes in the dataset
that were contained within a 20 MNI unit radius sphere centered on
that voxel.  We defined the \textit{density} at that location as this
proportion.  Across Datasets 1 and 2, the electrode placement
densities were similar (correlation by voxel:
$r = 0.56, p < 10^{-10}$).  We wondered whether regions with good
covererage might be associated with better reconstruction accuracy
(e.g. Fig.~\ref{fig:corrmap}C, D indicate that many electrodes in the
MTL have relatively high reconstruction accuracy, and occipital
electrodes tend to have relatively low reconstruction accuracy).  To
test whether this held more generally across the entire brain, for
each dataset we computed the electrode placement density for each
electrode from each patient (using the proportion of \textit{other}
patients' electrodes within 20 MNI units of the given electrode).  We
then correlated these density values with the across-patient
reconstruction accuracies for each electrode.  Contrary to our
expectation, rather than positive correlations, we found weak (but
reliable) negative correlations between reconstruction accuracy and
density for both datasets (Dataset 1: $r = -0.07, p < 10^{-5}$; Dataset 2:
$r = -0.18, p < 10^{-10}$).  This indicates that the reconstruction
accuracies we observed are not driven solely by sampling density, but
rather may also reflect higher order properties of neural dynamics
such as functional correlations between distant
voxels~\citep{BetzEtal17b}.

@@

To gain insights into whether particular electrode locations might be
especially informative, we first computed the average reconstruction
accuracy across all of each patient's electrodes (using the
across-patients cross validation test; black histograms in
Fig.~\ref{fig:corrmap}A and B).  We labeled each patient's electrodes
in each dataset with the average reconstruction accuracy for that
patient.  In other words, we assigned every electrode from each given
patient the same value, reflecting how well the activity patterns at
those electrodes were reconstructed on average.  Next, for each voxel
in the 4~mm$^3$ MNI brain, we computed the average value across any
electrode (from any patient) that came within 20 MNI units of that
voxel's center.  Effectively, we computed an \textit{information
  score} for each voxel, reflecting the average reconstruction
accuracy across any patients with electrodes near each voxel-- where
the averages were weighted to reflect patients who had more electrodes
implanted near that location. This yielded a single map for each
dataset, highlighting regions that are potentially promising
implantation targets in terms of providing full-brain activity
information via SuperEEG (Fig.~\ref{fig:informap}A, B).  Despite task
and patient differences across the two datasets, we nonetheless found
that the maps of the most promising implantation targets derived from
both datasets were similar (voxelwise correlation between information
scores across the two datasets: $r = 0.23, p < 10^{-10}$).  While the
correspondence between the two maps was not perfect, our finding that
there were some commonalities between the two maps lends support to
the notion that different brain areas are differently informative
about full-brain activity patterns.  Further, regions like the right post
central gyrus, right supramarginal gyrus,
and the right nucleus accumbens that exhibited strong information scores in both datasets may
be especially promising implantation targets.
